---
title: "Analytics Primer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Primer on analytics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(stablecoin)
```

## Analytics
Support for analytical queries is evolving.  Currently, this package supports some queries available through `Coin Metrics` and `BitQuery`.  Ethereum has the most robust services indexing smart contract events, and therefore most of the currently available functionality is specific to Ethereum.

### Historical Supply
Historical supply is currently limited to Ethereum tokens.  To query the historical supply of a stablecoin on Ethereum, utilize the `historical_supply()` function.
```{r}
df <- historical_supply(network = "Ethereum", 
                        token = "USDC", 
                        start_time = '2020-01-01', 
                        end_time = '2021-07-14')
tail(df)
```

### Algorand Analytics
Not yet available.  If you call the `historical_supply` function, you will get an error message.

### Ethereum Analytics
Ethereum analytics currently supports queries through Coin Metrics and BitQuery

#### Coin Metrics
Queries against the Coin Metrics community API are available through the `coinmetrics_query()` function interface.  For more information about the field definitions available through Coin Metrics, see their [documentation](https://docs.coinmetrics.io/api/v4)

Fetch and store the amount of daily active USDC supply on Ethereum in a tibble data frame.  Note that this function uses the Coin Metrics API field `SplyAct1d`.  Other metrics can also be substituted.
```{r}
df <- coinmetrics_asset_metrics(
                                token = "USDC", 
                                metric = "SplyAct1d", 
                                start_time = '2020-01-01', 
                                end_time = '2020-07-14')

tail(df)
```

An internal dataset holds the fields which are currently available through the Coin Metrics API.  To view the dataset, simply type `coinmetrics`.  The example below shows some of the supported fields:
```{r}
coinmetrics %>% select(id, description) %>% tail(n=5)
```

### Solana Analytics
Not yet available.  If you call the `historical_supply` function, you will get an error message.

### Stellar Analytics
Not yet available.  If you call the `historical_supply` function, you will get an error message.

### TRON Analytics
Not yet available.  If you call the `historical_supply` function, you will get an error message.
