---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE, message=FALSE, warning=FALSE}
library(stablecoin)
library(scales)
```

## Current Supply
Utilize the `tokens` data object to see a current list of the tokens and networks that are supported by this package.  The `historical` boolean indicates whether historical queries are supported.

```{r, echo = FALSE, results='asis'}
tokens %>%
  select(network, token, historical, token_id) %>%
  knitr::kable(., caption = "Supported Stablecoins")
```

To query the supply of USDC on a particular blockchain, utilize the `current_supply()` function  Fetching the Ethereum USDC circulation is shown below:
```{r}
current_supply(network = "Ethereum", token = "USDC")
```

### Multiple Blockchains
To query the balance of a stablecoin on supported blockchains, simply utilize the `current_supply_all()` functions.  Fetching the total supply of USDC and USDT is shown below:
```{r}
current_supply_all(selected_tokens = c("USDC", "USDT"))
```
